\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-01-27 motivation.tex
Added proofs, can talk a bit more about completeness and soundness

\subsubsection{Programming using the non exact real-time control
  construct the \textrm{\texttt{wait\_inbetween}} statement}
\label{sec:progr-using-non}

@@

Consider a machine used to test human response time and collect this
data for future research purposes. The machine switches on a green light
on a touch screen for anywhere between 50.3 ms to 200.3 ms, if the user
can touch this green light then she is successful and an integer
\texttt{1} is sent to a database, if unsuccessful a \texttt{0} is sent
instead. Different statistics and analyses on human responsiveness can
be based on the collected data.

@@

The SystemJ program is divided into two clock-domains, the first
clock-domain continuously displays a green light (\texttt{GREEN\_LIGHT}
signal) on the touch screen sensor and waits for the user to respond. If
the user is able to touch the screen within the specified time of 50.3
ms to 200.3 ms a positive response is sent to the second
clock-domain. All the SystemJ programming constructs used to implement
this system are described in~\cite{amal10} and Table~\ref{tab:1}. The
\texttt{wait\_inbetween} specification, which models the non exact delay
between 50.3 ms and 200.3 ms is not supported in the current language
and cannot be compiled with the current SystemJ compiler. We introduce
real-time \texttt{wait\_inbetween} statements in SystemJ. Such non exact
real-time mechanisms are useful in developing systems where the
real-time delay is not know or should not be known a priori.

\subsubsection{Programming a timeout using the non exact real-time
  construct the \texttt{wait\_atleast} statement}
\label{sec:progr-time-using}

@@

\subsubsection{Programming periodic tasks using the exact real-time
  construct the \texttt{wait\_exactly} statement}
\label{sec:progr-using-exact}

@@

\begin{figure}[t!]
  \centering
	\vspace{-10pt}
        \begin{SubFloat}{\label{pp:a}Periodically emitting signal S}
        \begin{lstlisting}[style=sysj,morekeywords={emit,trap,pause,exit,wait_exactly}]
while(true) { 
 wait_exactly (1 ms); 
 emit S; 
 //do something 
}
\end{lstlisting}
\end{SubFloat}
\begin{SubFloat}{\label{pp:b}Timing diagram -- the X-axis shows the
    execution of the \texttt{wait\_exactly} statement. The Y-axis is the
    time elapsed.}
  \includegraphics[scale=0.7]{FF3}
\end{SubFloat}
  \caption{Programming a periodic task with wait\_exactly}
  \label{fig:periodic}
  \vspace{-10pt}
\end{figure}

One such example; periodic emission of a signal to the environment is
shown in Figure~\ref{fig:periodic}. As before upon execution of
\texttt{wait\_exactly (1 ms)} statement, the time starts elapsing. But,
unlike in previous cases the following statement needs to be executed
once 1 ms have passed, as shown in Figure~\ref{pp:b}.

>>>>

\subsubsection{Programming using the non exact real-time control
  construct; the \textrm{\texttt{wait\_inbetween}} statement}
\label{sec:progr-using-non}

@@

Consider a machine used to test human response time and collect this
data for future research purposes. The machine switches on a green light
on a touch screen for anywhere \textit{in between} 50.3 ms to 200.3 ms,
if the user can touch this green light then she is successful and an
integer \texttt{1} is sent to a database, if unsuccessful a \texttt{0}
is sent instead. Different statistics and analyses on human
responsiveness can be based on the collected data.

@@

The SystemJ program is divided into two clock-domains, the first
clock-domain continuously displays a green light (\texttt{GREEN\_LIGHT}
signal) on the touch screen sensor and waits for the user to respond. If
the user is able to touch the screen within the specified time of 50.3
ms to 200.3 ms a positive response is sent to the second
clock-domain. All the SystemJ programming constructs used to implement
this system are described in~\cite{amal10} and Table~\ref{tab:1}. The
\texttt{wait\_inbetween} specification, which models the non exact delay
between 50.3 ms and 200.3 ms is not supported in the current language
and cannot be compiled with the current SystemJ compiler. We introduce
such \texttt{wait\_inbetween} statements in SystemJ. Such non exact
real-time mechanisms are useful in developing systems where the
real-time delay is not known or should not be known a priori.

\subsubsection{Programming a timeout using the non exact real-time
  construct; the \texttt{wait\_atleast} statement}
\label{sec:progr-time-using}

@@

\subsubsection{Programming periodic tasks using the exact real-time
  construct; the \texttt{wait\_exactly} statement}
\label{sec:progr-using-exact}

@@

\begin{figure}[t!]
  \centering
	\vspace{-10pt}
        \begin{SubFloat}{\label{pp:a}Periodically emitting signal S}
        \begin{lstlisting}[style=sysj,morekeywords={emit,trap,pause,exit,wait_exactly}]
while(true) { 
 wait_exactly (1 ms); 
 emit S; 
 //do something 
}
\end{lstlisting}
\end{SubFloat}
\begin{SubFloat}{\label{p1:b}Timing diagram -- the X-axis shows the
    execution of the \texttt{wait\_exactly} statement. The Y-axis is the
    time elapsed.}
  \includegraphics[scale=0.7]{FF3}
\end{SubFloat}
  \caption{Programming a periodic task with wait\_exactly}
  \label{fig:p1}
  \vspace{-10pt}
\end{figure}

One such example; periodic emission of a signal to the environment is
shown in Figure~\ref{fig:p1}. As before upon execution of
\texttt{wait\_exactly (1 ms)} statement, the time starts elapsing. But,
unlike in previous cases the following statement needs to be executed
exactly after 1 ms have passed, as shown in Figure~\ref{p1:b}.

### 2014-01-27 related_work.tex
Added proofs, can talk a bit more about completeness and soundness

A number of studies have been performed when it comes to integrating
real-time directly as a programming construct in GALS (and its subset
synchronous) reactive languages. The most prominent works in this area
are by Shyamsundar~\cite{rsh94} and Bourke et
al.~\cite{Bourke2009a}. Shyamsundar incorporates real-time using
external timers in \textit{Communicating Reactive Processes} (CRP),
which like SystemJ is an extension of synchronous language Esterel to
asynchorny. But, as mentioned in Section~\ref{sec:inter-timers-react}
and~\ref{sec:resolution-real-time} external timers do not interact well
with preemption constructs in these languages. Bourke et al. introduce
real-time as first class constructs in the Esterel language. They like
us provide real-time wait statements called \texttt{delay} as first
class Esterel programming constructs, and translate them into Esterel
kernel constructs. But, unlike us they do not translate wait statements
into \texttt{pause} constructs directly. Instead, logical ticks are
generated by using abstract notion of \texttt{event} and \texttt{sample}
platform dependent timers. This notion makes it a complex and inflexible
solution since the number of platform timers with certain resolutions
need to be determined and present on the system for the solution to be
realizable. Moreover, non exact real-time waits and integration with
non-maximal parallelism is not studied at all. Our solution does not
require external timers (like~\cite{rsh94}) or logical notion of timers
(like~\cite{Bourke2009a}). In our solution we calculate the real-time
waiting time in logical ticks \textit{after} allocation and scheduling,
it gives the compiler developers the chance to optimize for many
different criteria such as computation time, energy, power, etc, without
worrying about or violating the real-time wait specification.

>>>>

A number of studies have been performed when it comes to integrating
real-time directly as a programming construct in GALS (and its subset
synchronous) reactive languages. The most prominent works in this area
are by Shyamsundar~\cite{rsh94} and Bourke et
al.~\cite{Bourke2009a}. Shyamsundar incorporates real-time using
external timers in \textit{Communicating Reactive Processes} (CRP),
which like SystemJ is an extension of synchronous language Esterel to
asynchorny. But, as mentioned in Section~\ref{sec:inter-timers-react}
and~\ref{sec:resolution-real-time} external timers do not interact well
with preemption constructs in these languages. Bourke et al. introduce
real-time as first class constructs in the Esterel language. They like
us provide real-time wait statements called \texttt{delay} as first
class Esterel programming constructs, and translate them into Esterel
kernel constructs. But, unlike us they do not translate wait statements
into \texttt{pause} constructs directly. Instead, logical ticks are
generated by using abstract notion of \texttt{event} and \texttt{sample}
platform dependent timers. This notion makes it a complex and inflexible
solution since the number of platform timers with certain resolutions
need to be determined and present on the system for the solution to be
realizable. Moreover, non exact real-time waits and integration with
non-maximal parallelism is not studied at all. Our solution does not
require external timers (like~\cite{rsh94}) or logical notion of timers
(like~\cite{Bourke2009a}). In our solution we calculate the real waiting
time in logical ticks \textit{after} allocation and scheduling, it gives
the compiler developers the chance to optimize for many different
criteria such as computation time, energy, power, etc, without worrying
about or violating the real-time wait specification.
